---
title: "Data Cleaning"
author: '26820228'
date: "10/08/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# **Setup** #

```{r setup}

knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "~/Library/Mobile Documents/com~apple~CloudDocs/Documents/Uni/Masters/Empirical Project/Code/Empirical_Project")

# turn off scientific notation
options(scipen = 999)

```

### *Load Libraries* ###

```{r set libraries}

library("dplyr") # for mutate function
library("reshape2") # for transforming data into wide and long format
library("tidyverse") # for tidying data 
library("readr") # to read in data 

```

### *Set Working Directory* ###

```{r set working directory}

# please change this to your own working directory path
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/Uni/Masters/Empirical Project/Code/Empirical_Project")

```

# **Fixation Data** #

## *Read in Fixation Data and Save Data to an Object* ##

```{r read fixation file and save data to an object}

# please change this to however you have stored the data file 
df_fixations <- read.csv(file = "data/fixation_report.csv", header = TRUE, na.strings = ".")

```

## *Tidy / Check Fixation Dataset* ##

```{r tidy / check fixation dataset}

# retain only necessary columns
df_fixations <- data.frame(df_fixations[ , c("RECORDING_SESSION_LABEL", 
                                             "TRIAL_INDEX",  "trial", "ext",
                                             "CURRENT_FIX_START", "CURRENT_FIX_END",
                                             "CURRENT_FIX_DURATION")])

# rename columns for easier interpretation
colnames(df_fixations) <- c("id", "trial_number", "condition", "extinction", 
                            "fix_start", "fix_end", "fix_duration")

# and re-arrange by participant number (first to last)
df_fixations <- df_fixations %>% 
  arrange(id)

# exclude CS-US trials
df_fixations <- df_fixations[df_fixations$condition != 3, ]

# retain only fixations that begin within 4000ms 
# as these will begin within the stimulus presentation period
df_fixations <- data.frame(df_fixations[df_fixations$fix_start < 4000, ])

```

## *Compute Fixation Duration Averages* ##

```{r compute fixation duration averages}

#### for conditions 4, 5, 6 & 7 (acquisition CS+ & CS-, extinction CS+ & CS-)
# get the mean fixation duration for each participant for each trial 
df_fix_duration <- df_fixations %>% 
  group_by(id, trial_number, condition) %>%
  summarise(mean_fix_duration = mean(fix_duration))

# get the mean fixation duration of the average fixation duration for 
# each participant trial for each condition
df_fix_duration <- df_fix_duration %>% 
  group_by(id, condition) %>% 
  summarise(mean_fix_condition = mean(mean_fix_duration))

# transform to wide format
df_fix_duration_wide <- pivot_wider(df_fix_duration,
                                id_cols = c(id, condition),
                                names_from = condition,
                                values_from = mean_fix_condition)


# rename columns for easier interpretation
colnames(df_fix_duration_wide) <- c("id", "acq_csp_fix_duration", 
                                         "acq_csm_fix_duration", 
                                         "ext_csp_fix_duration",
                                         "ext_csm_fix_duration") 


#### now for early (cond 8) and late (cond 9) extinction 
# get the mean fixation duration for each participant for each trial 
df_fix_duration_extinction <- df_fixations %>% 
  filter(extinction == 8 | extinction == 9) %>% 
  group_by(id, trial_number, condition, extinction) %>%
  summarise(mean_fix_duration_extinction = mean(fix_duration))

# get the mean fixation duration of the average fixation duration for 
# each participant trial for each condition
df_fix_duration_extinction <- df_fix_duration_extinction %>% 
  group_by(id, condition, extinction) %>% 
  summarise(mean_fix_condition_extinction = mean(mean_fix_duration_extinction))

# transform to wide format
df_fix_duration_extinction_wide <- pivot_wider(df_fix_duration_extinction,
                                id_cols = c(id, condition, extinction),
                                names_from = c(condition,extinction),
                                values_from = mean_fix_condition_extinction)


# rename the columns for easier interpretation
colnames(df_fix_duration_extinction_wide) <- c("id", "e_ext_csp_fix_duration", 
                                         "l_ext_csp_fix_duration", 
                                         "e_ext_csm_fix_duration", 
                                         "l_ext_csm_fix_duration") 

```

## *Compute Fixation Count Averages* ##

```{r compute fixation count averages}

#### for conditions 4, 5, 6 & 7 (acquisition CS+ & CS-, extinction CS+ & CS-)

# obtain fixation count per participants per trial 
df_fix_count <- df_fixations %>%
  group_by(id, trial_number, condition) %>%
  summarise(fix_count = length(fix_start))

# get the mean fixation count for each participant for each condition
df_fix_count <- df_fix_count %>% 
  group_by(id, condition) %>% 
  summarise(mean_fix_condition = mean(fix_count))

# transform to wide format
df_fix_count_wide <- pivot_wider(df_fix_count,
                                id_cols = c(id, condition),
                                names_from = condition,
                                values_from = mean_fix_condition)


# rename columns for easier interpretation
colnames(df_fix_count_wide) <- c("id", "acq_csp_fix_count", 
                                         "acq_csm_fix_count", 
                                         "ext_csp_fix_count",
                                         "ext_csm_fix_count") 


#### now for early (cond 8) and late (cond 9) extinction 
# obtain fixation count for each participant for each trial 
df_fix_count_extinction <- df_fixations %>% 
  filter(extinction == 8 | extinction == 9) %>% 
  group_by(id, trial_number, condition, extinction) %>%
  summarise(fix_count = length(fix_start)) 

# get the mean fixation count for each participant for each condition
df_fix_count_extinction <- df_fix_count_extinction %>% 
  group_by(id, condition, extinction) %>% 
  summarise(mean_fix_condition_extinction = mean(fix_count))

# transform to wide format
df_fix_count_extinction_wide <- pivot_wider(df_fix_count_extinction,
                                id_cols = c(id, condition, extinction),
                                names_from = c(condition,extinction),
                                values_from = mean_fix_condition_extinction)


# rename the columns for easier interpretation
colnames(df_fix_count_extinction_wide) <- c("id", "e_ext_csp_fix_count", 
                                         "l_ext_csp_fix_count", 
                                         "e_ext_csm_fix_count", 
                                         "l_ext_csm_fix_count") 

```

# **Saccade Data** #

## *Read in Saccade Data and Save Data to an Object* ##

```{r read saccade file and save data to an object}

# please change this to however you have stored the data file 
df_saccades <- read.csv(file = "data/saccade_report.csv", header = TRUE, na.strings = ".")

```

## *Tidy / Check Dataset* ##

```{r tidy / check saccade dataset}

# retain only necessary columns
df_saccades <- data.frame(df_saccades[ , c("RECORDING_SESSION_LABEL", 
                                             "TRIAL_INDEX",  "trial", "ext",
                                             "CURRENT_SAC_START_TIME", 
                                           "CURRENT_SAC_END_TIME", 
                                             "CURRENT_SAC_AMPLITUDE")])

# rename columns for easier interpretation
colnames(df_saccades) <- c("id", "trial_number", "condition", "extinction", 
                           "sacc_start", "sacc_end", "sacc_amplitude")

# and re-arrange by participant number (first to last)
df_saccades <- df_saccades %>% 
  arrange(id)

 # retain only saccades that begin within 4000ms 
# as these will begin within the stimulus presentation period
df_saccades <- data.frame(df_saccades[df_saccades$sacc_start < 4000, ])

# exclude CS-US trials
df_saccades <- df_saccades[df_saccades$condition != 3, ]

```

## *Compute Saccade Amplitude Averages* ##

```{r compute saccade averages}

#### for conditions 4, 5, 6 & 7 (acquisition CS+ & CS-, extinction CS+ & CS-)

# get the mean saccade amplitude for each participant for each trial 
df_sacc_amplitude <- df_saccades %>% 
  group_by(id, trial_number, condition) %>%
  summarise(mean_sacc_amplitude = mean(sacc_amplitude), na.rm = TRUE)

# get the mean saccade amplitude of the average saccade amplitude for 
# each participant trial for each condition
df_sacc_amplitude <- df_sacc_amplitude %>% 
  group_by(id, condition) %>% 
  summarise(mean_sacc_amplitude_condition = mean(mean_sacc_amplitude), na.rm = TRUE) 

# transform to wide format
df_sacc_amplitude_wide <- pivot_wider(df_sacc_amplitude,
                                id_cols = c(id, condition),
                                names_from = condition,
                                values_from = mean_sacc_amplitude_condition)


# rename columns for easier interpretation
colnames(df_sacc_amplitude_wide) <- c("id", "acq_csp_sacc_amplitude", 
                                         "acq_csm_sacc_amplitude", 
                                         "ext_csp_sacc_amplitude",
                                         "ext_csm_sacc_amplitude") 


#### now for early (cond 8) and late (cond 9) extinction 
# get the mean saccade amplitude for each participant for each trial 
df_sacc_amplitude_extinction <- df_saccades %>% 
  filter(extinction == 8 | extinction == 9) %>% 
  group_by(id, trial_number, condition, extinction) %>%
  summarise(mean_sacc_amplitude_extinction = mean(sacc_amplitude))

# get the mean saccade amplitude of the average saccade amplitude for 
# each participant trial for each condition
df_sacc_amplitude_extinction <- df_sacc_amplitude_extinction %>% 
  group_by(id, condition, extinction) %>% 
  summarise(mean_sacc_amplitude_condition_extinction = mean(mean_sacc_amplitude_extinction))

# transform to wide format
df_sacc_amplitude_extinction_wide <- pivot_wider(df_sacc_amplitude_extinction,
                                id_cols = c(id, condition, extinction),
                                names_from = c(condition,extinction),
                                values_from = mean_sacc_amplitude_condition_extinction)


# rename the columns for easier interpretation
colnames(df_sacc_amplitude_extinction_wide) <- c("id", "e_ext_csp_sacc_amplitude", 
                                         "l_ext_csp_sacc_amplitude", 
                                         "e_ext_csm_sacc_amplitude", 
                                         "l_ext_csm_sacc_amplitude") 

```

# **Questionnaire and Demographic Data** #

## *Read in Questionnaire Data and Save Data to an Object* ##

```{r read questionnaire data file and save data to an object}

# please change this to however you have stored the data file 
df_questionnaires <- read.csv(file = "data/questionnaires.csv", header = TRUE, na.strings = ".")

```

## *Read in Demographics Data and Save Data to an Object* ##

```{r read demographics data file and save data to an object}

# please change this to however you have stored the data file 
df_demographics <- read.csv(file = "data/demographics.csv", header = TRUE, na.strings = ".")

```

## *Code the Demographic Data* ##

```{r code demographics}

df_demographics <- df_demographics %>%
  mutate(sex = recode(sex,
                      "Female (Gender: Male)" = "Female")) %>%
  mutate(ethnicity = recode(ethnicity,
                            "Asian" = "Asian",
                            "Asian- Malaysian Chinese" = "Asian",
                            "Asian- Chinese" = "Asian",
                            "Chinese" = "Asian",
                            "Asian - Pakistani" = "Asian",
                            "Asian (Pakistani)" = "Asian",
                            "Pakistan" = "Asian",
                            "British Pakistani" = "Asian",
                            "Indian" = "Asian",
                            "Malay" = "Asian",
                            "SriLanken" = "Asian",
                            "British Asian (Indian)" = "Asian",
                            "Kazakh" = "Asian",
                            "Black" = "Black",
                            "Black African" = "Black",
                            "Middle Eastern/ Arab" = "Middle Eastern/ Arab",
                            "Arab- North African" = "Middle Eastern/ Arab",
                            "Arab" = "Middle Eastern/ Arab",
                            "Mixed White/ Asian" = "Mixed",
                            "White/ Asian" = "Mixed",
                            "Half British, Half Asian" = "NA",
                            "White" = "White",
                            "White- other" = "White",
                            "White- Caucasian" = "White",
                            "British White" = "White",
                            "Caucasian" = "White",
                            "White Other" = "White",
                            "White British" = "White",
                            "white" = "White",
                            "British (white)" = "White",
                            "British" = "NA",
                            "Bulgarian" = "NA",
                            "Greek Cypriot" = "NA",
                            "Greek" = "NA",
                            "Russian" = "NA")) %>%
  mutate(sexual_orientation = recode(sexual_orientation,
                                     "Heterosexual" = "Heterosexual",
                                     "Straight" = "Heterosexual",
                                     "Straight Woman" = "Heterosexual",
                                     "Straight/ Heterosexual" = "Heterosexual",
                                     "Male" = "Heterosexual",
                                     "Gay" = "Sexual Minority",
                                     "Gay Man" = "Sexual Minority",
                                     "Bisexual" = "Sexual Minority",
                                     "Bisexual/Queer" = "Sexual Minority",
                                     "Lesbian" = "Sexual Minority",
                                     "Lesbian/ Queer" = "Sexual Minority",
                                     "Pansexual" = "Sexual Minority"))

```

# **Bind the Data** #

```{r bind the data}

# bind the data (for all participants)
dataframe_1 <- cbind(df_fix_duration_wide, df_fix_duration_extinction_wide, 
                     df_fix_count_wide, df_fix_count_extinction_wide, 
                     df_sacc_amplitude_wide,df_sacc_amplitude_extinction_wide, 
                     df_questionnaires, df_demographics)

# remove repeated participant id columns
dataframe_1 <- dataframe_1[ , -c(6, 11, 16, 21, 26, 31, 80)]

# rename columns again
colnames(dataframe_1)[1] <- "id"

# create subdf for all participants except 'definitely exclude'
dataframe_2 <- dataframe_1[-c(2, 74, 101, 102, 110), ]

# create subdf for good AOI data participants only
dataframe_3 <- dataframe_1[c(8, 9, 13, 14, 16, 29, 30, 32, 37, 38, 40, 45, 46, 
                             48, 51, 53, 63, 64, 68, 69, 79, 100, 104, 107, 
                             108, 121, 129, 131), ]

# and write each to csv
write.csv(dataframe_1, "data/cleaned/dataframe_1.csv", row.names = FALSE)
write.csv(dataframe_2, "data/cleaned/dataframe_2.csv", row.names = FALSE)
write.csv(dataframe_3, "data/cleaned/dataframe_3.csv", row.names = FALSE)

```
